---
ntitle: "Markdown Snippet"
date: "31 August 2015"
output: html_document
---

Getting started with Markdown
---
---

Text in markdown documents can be written in without any specific notation.   
That is; you don't need to 'tell' R it is text.

---

> Three dashes denotes a break in the text  
> `>` creates a block quote  
> Two spaces after a sentace starts a new line  

---

> The hashtag (#) is used to denote size of header. E.g;

## Papa bear
#### Mama bear
###### Baby bear

---

> We use asterisks to create *italics* and **bold** face

---

> Lists can be created using an asterisk or a number.

### What's in my kitchen?
* Pizza
* Wine
* Doughnuts

> `+` after two tabs denotes sub-items
 
1. Pizza
    + Margherita
    + Funghi
2. Wine
    + Pinot Grigio
    + Chianti
3. Doughnuts
    + All the doughnuts
 
---

> Horizontal and vertical dashes create tables

Variable 1 | Variable 2 | Variable 3
-----------|------------|------------
obs 1      | obs 3      | obs 5
obs 2      | obs 4      | obs 6

We can later add 

---

> To interface with R language, we add code in 'chunks'. 


```{r}
summary(iris)
```

---

By adding the `echo = FALSE` parameter, R code is not added to the knitted document, only the output.  
This can be useful for embedding plots...

```{r, echo = FALSE}
library(ggplot2)
data(iris)
p <- ggplot(iris, aes(x = Sepal.Width, y = Petal.Length)) + geom_point(aes(colour = Species)) +
  geom_abline(colour = 'red') +
  labs(title = "Sepal Width vs Petal Length")

p
```

---

Maybe you want to let your collaborators see all of the code you have used, and all outputs.  
To show which packages/error distributions/ link functions or any other decisions you have made.  

```{r}
mod1 <- lm(Petal.Length ~ Petal.Width + Sepal.Length +Sepal.Width, data=iris)
summary(mod1)
plot(mod1)
```

> Markdown makes it easy to add comments and annotations about your analysis in the early stages of your project. 
